    %-------------------------
% Resume in Latex
% Author
% License : MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Shikhar Pratap Singh} % Your Name
\newcommand{\course}{Computer Science  } % Your Program
\newcommand{\roll}{2100320120156} % Your Roll No.
\newcommand{\phone}{9015061999} % Your Phone Number
\newcommand{\emaila}{shikharpsingh1@gmail.com} %Email 1

\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------

{
\begin{tabularx}{\linewidth}{L r} \\
  \textbf{\Large \name} & {\raisebox{0.0\height}{\footnotesize \faPhone}\ +91-\phone}\\
  {Roll No.: \roll } & \href{mailto:\emaila}{\raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\emaila}} \\
  Bachelor of Technology & \href{https://leetcode.com/cratesium/}{\raisebox{0.0\height}{\footnotesize \faCode}\ {https://leetcode.com/cratesium/}} \\
  {Abes Engineering College, Ghaziabad} & \href{https://www.hackerrank.com/profile/csc_2021b0121053}{\raisebox{0.0\height}{\footnotesize \faTerminal}\ {https://www.hackerrank.com/profile/csc_2021b0121053}} \\
  & \href{https://github.com/cratesium}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {https://github.com/cratesium}} \\
  & \href{https://www.linkedin.com/in/shikhar-pratap-singh-09a9b322a/}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {https://www.linkedin.com/in/shikhar-pratap-singh-09a9b322a/}} \\
\end{tabularx}
}




%-----------EDUCATION-----------
\section{\textbf{Education}}
\resumeSubHeadingListStart
    \resumeSubheading
      {High School}{Percentage : 86.2}
      {Karl Huber School, Noida}{2017-18}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {Intermediate}{Percentage : 71.2}
      {Karl Huber School, Noida}{2019-20}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Technology in Computer Science }{CGPA: 7.9}
      {ABES Engineering College, Ghaziabad}{2021-25}
  \resumeSubHeadingListEnd
\vspace{-5.5mm}
%
%-----------PROJECTS-----------------}
\section{\textbf{Projects}}
\resumeSubHeadingListStart
    \resumeProject
      {ABES Solutions} %Project Name
      {A project aimed at enhancing India's primary sector by providing farmers with centralized access to agricultural resources and information.} %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {Empowers farmers with vital resources like government schemes, soil analysis, and community development tools.}
        \item {Built with React and Spring Boot for efficient data management and user interaction.}
    \resumeItemListEnd
    \vspace{-2mm}

    \resumeProject
      {Realtime Chat App} %Project Name
      {A HTML based web application which allow users to chat in real time. } %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {Frontend: HTML, CSS, JavaScript, Bootstrap}
        \item {Backend: Spring Boot simplifies setting up a backend server for handling user authentication, database interaction, and message routing.}
        \item {Firebase: Provides Cloud Firestore for storing chat data and Realtime Database for real-time updates, enabling instant message display.}
    \resumeItemListEnd
    \vspace{-2mm}

    \resumeProject
      {Notepad} %Project Name
      {A Java Swing-based application providing a graphical user interface (GUI) for text editing and note-taking.} %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {Utilizes Java Swing for creating a user-friendly interface with features like text input and editing.}
        \item {Enables users to create, edit, and save text documents conveniently on their desktop.}
    \resumeItemListEnd
    \vspace{-2mm}

    \resumeProject
      {Snake Game} %Project Name
      {The game is built using Java Swing, providing a simple graphical user interface (GUI) for the player to interact with.} %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {Classic Gameplay: Control a snake to eat apples and grow longer.}
        \item {Avoid Collisions: Navigate carefully to prevent collisions with walls or the snake itself.}
        \item {Objective: Grow the snake as long as possible while avoiding obstacles to achieve a high score.}
    \resumeItemListEnd
    \vspace{-2mm}

  \resumeSubHeadingListEnd
\vspace{2mm}

%-----------EXPERIENCE-----------------

\section{\textbf{Technical Skills and Interests}}
 \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, JAVA Core, Javascript, HTML+CSS,Python (Basic)  } \\
     \textbf{Libraries }{: C++ STL, ReactJs }\\ 
     \textbf{Web Dev Tools}{: Eclipse, VScode, Git, Github } \\ 
     \textbf{Frameworks}{: ReactJs ,SpringBoot} \\
     \textbf{Cloud/Databases}{:MongoDb,  Oracle } \\  
     
     \textbf{Relevent Coursework}{: Data Structures \& Algorithms, Operating Systems, Object Oriented Programming, Database Management System, Software Engineering. } \\ 
     \textbf{Areas of Interest}{: Web Design and Development ,Data Structure and Algorithms.} \\
     \textbf{Soft Skills}{: Problem Solving, Self-learning, Presentation, Adaptability} \\
    }}
 \end{itemize}
 \vspace{-16pt}

\section{\textbf{Certifications}}
\resumeSubHeadingListStart
    \resumeSubItem{Data Structure and Backend With Java }{Board Infinity}
    \resumeSubItem{Introduction to Frontend }{Meta}
        \resumeSubItem{Problem Solving (Basic) }{HackerRank}
    \resumeSubItem{Problem Solving (Intermediate) }{HackerRank}
    \resumeSubItem {PCAP: Programming Essentials in Python}{Cisco Networking Academy & openEDG python institute}
    \resumeSubItem{CPA: Programming Essentials in C++ }{OpenEDG C++}
    \resumeSubItem{Python (Basic) }{HackerRank}

    % Add more certifications as needed
\resumeSubHeadingListEnd




\section{\textbf{Positions of Responsibility}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\resumePOR{ ACM  Core Member} % Position
    {ABES Engineering College} %Club,Event
    {} %Tenure Period \\
    \resumeItemListStart
    \item {Helped to conduct many events inside the campus}
    \resumeItemListEnd
    \resumePOR{ Camp Coordinator} % Position
    {LDL} %Club,Event
    {} %Tenure Period \\
    \resumeItemListStart
    \item {I volunteered as a teacher, imparting knowledge to those unable to afford formal education.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-5mm}





% %-----------Achievements-----------------
% \section{\textbf{Achievements}}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year
    
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year
% \resumeSubHeadingListEnd
% \vspace{-5mm}



%-------------------------------------------
\end{document}
